INTELLIGENT SYSTEMS

### 2021-04-08 paper_5.tex
working on 5.4.4

    \item \emph{Single Task with Fusion} (1 Task, + Sensor): in this experiment 3 CNNs 
    are used, one for each task, each making up a branch. In this case, the 
    combination of data from different sensors will be useful to be able to 
    determine only 1 task and therefore only one class. The results obtained 
    are better than the previous points, except for the gender class where 
    the MultiTask approach achieves a better score.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c||ccc|c||ccc|c|}
            \hline
                & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
            \hline
                Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
            \hline
                SingleTask Fusion & 94.2 & 95.0 & 95.6 & 94.9 & 93.5 & 95.0 & 95.6 & 94.7\\
            \hline 
        \end{tabular}
        \end{adjustbox}
        \caption{Accuracy and F1-score (1 Task, + Sensor).}
        \label{table accuracy and F1 (1 Task, + Sensor)}
    \end{table}
\end{enumerate}

>>>>

    \item \emph{Single Task with Fusion} (1 Task, + Sensor): in this experiment 3 CNNs 
    are used, one for each task, each making up a branch. In this case, the 
    combination of data from different sensors will be useful to be able to 
    determine only 1 task and therefore only one class. The results obtained 
    are better than the previous points, except for the gender class where 
    the MultiTask approach achieves a better score.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c||ccc|c||ccc|c|}
            \hline
                & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
            \hline
                Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
            \hline
                SingleTask Fusion & 94.2 & 95.0 & 95.6 & 94.9 & 93.5 & 95.0 & 95.6 & 94.7\\
            \hline 
        \end{tabular}
        \end{adjustbox}
        \caption{Accuracy and F1-score (1 Task, + Sensor).}
        \label{table accuracy and F1 (1 Task, + Sensor)}
    \end{table}

    \item \emph{Multi-task with Fusion} (+ Task, + Sensor): the last experiment consists in applying the fusion in a multitasking context within the network. In this case it will be necessary to train a CNN for all three existing tasks. From the results shown in table \ref{table accuracy and F1 (+ Task, + Sensor)}, this architecture manages to achieve better performance than the others mentioned above, this is because the model has much more information (labels and inputs) to describe people. The strength of this architecture is that it manages to return a result for each task.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c||ccc|c||ccc|c|}
            \hline
                & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
            \hline
                Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
            \hline
                MultiTask Fusion & \bfseries{94.8} & \bfseries{96.1} & \bfseries{97.7} & \bfseries{96.2} & \bfseries{93.8} & \bfseries{96.3} & \bfseries{97.7} & \bfseries{95.9}\\
            \hline 
        \end{tabular}
        \end{adjustbox}
        \caption{Accuracy and F1-score (1 Task, + Sensor).}
        \label{table accuracy and F1 (+ Task, + Sensor)}
    \end{table}

\end{enumerate}
